Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2024-07-04 manuscript/manuscript.Rmd
Update manuscript.Rmd

Robust location- and scale-invariant transformations are realised by simultaneously optimising three parameters, i.e. transformation parameter $\lambda$, shift parameter $x_0$ and scale parameter $s$, using maximum likelihood optimisation.
It is feasible that standardisation of a numeric variable (e.g., through subtracting its median value and division by its interquartile range) prior to conventional transformations may achieve a similar effect in mitigating sensitivity to the distribution's location and scale.

@@

>>>>

Robust location- and scale-invariant transformations are realised by simultaneously optimising three parameters, i.e. transformation parameter $\lambda$, shift parameter $x_0$ and scale parameter $s$, using maximum likelihood optimisation.
Alternatively, standardisation of a numeric variable (e.g., through subtracting its median value and division by its interquartile range) prior to conventional power transformations may achieve a similar effect in reducing sensitivity to the distribution's location and scale.

This study had the following limitations.
First, in our experimental results we focussed on the Yeo-Johnson transformation because of its ability to handle variables with negative values, and did not consider the Box-Cox transformation.
Likewise, we focussed on maximum likelihood estimation to optimise parameters, and did not investigate other metrics to the same extent, due to lack of demonstrable benefit (Appendix B).

@@

Robust location- and scale-invariant power transformations allow for automated power transformation of numerical variables/
